A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
OK I checked it
MIP

Maximum common subgraph problems are NP-hard, and remain challenging
computationally. Recent practical progress has been made by using constraint
programming \citep{DBLP:conf/cp/NdiayeS11,DBLP:conf/cp/McCreeshNPS16}, by
reducing to the maximum clique problem
\citep{LeviG,DBLP:conf/cp/McCreeshNPS16}, and by adapting subgraph isomorphism
algorithms \citep{UpcomingAAAIPaper}. This paper introduces a new branch and
bound algorithm which exploits special properties of these problems to allow a
much faster exploration of the search space, whilst retaining the filtering and
bounding benefits of the constraint programming approach. We describe the
algorithm for the basic maximum common subgraph problem, and discuss how it may
be adapted to handle vertex labels, edge labels, and the requirement that the
found subgraph be connected. We then present an empirical study of the
algorithm, demonstrating that it improves the state of the art by more than an
order of magnitude on the unlabelled variant of the problem, and showing that
it can handle much larger instances than earlier constraint programming or
clique approaches due to lower memory usage.

@@

A further advantage of our encoding is that it gives us efficient access to a
better branching heuristic. The CP-FC algorithm uses smallest domain first,
which in our algorithm corresponds to branching on a label class with smallest
$|T|$. We instead branch on the label class with smallest $\min(|P|,|T|)$.
This is empirically better, and accounts for much of the difference between
the number of recursive calls made; branching on the smallest $|P| |T|$ gives
very similar results. This can be viewed as exploiting both smallest domain first,
and the dual viewpoint \citep{DBLP:conf/ecai/Geelen92} of smallest domain
first, simultaneously, but we do not have the overheads of having to maintain
and channel between the dual viewpoint that would be required when using a
conventional domain store. ?? Check this!

>>>>

Maximum common subgraph problems are NP-hard, and remain challenging
computationally. Recent practical progress has been made by using constraint
programming \citep{DBLP:conf/cp/NdiayeS11,DBLP:conf/cp/McCreeshNPS16} and
mathematical programming \citep{DBLP:journals/dam/BahienseMPS12}, by reducing
to the maximum clique problem \citep{LeviG,DBLP:conf/cp/McCreeshNPS16}, and by
adapting subgraph isomorphism algorithms \citep{UpcomingAAAIPaper}. This paper
introduces a new branch and bound algorithm which exploits special properties
of these problems to allow a much faster exploration of the search space,
whilst retaining the filtering and bounding benefits of the constraint
programming approach. We describe the algorithm for the basic maximum common
subgraph problem, and discuss how it may be adapted to handle vertex labels,
edge labels, and the requirement that the found subgraph be connected. We then
present an empirical study of the algorithm, demonstrating that it improves the
state of the art by more than an order of magnitude on the unlabelled variant
of the problem, and showing that it can handle much larger instances than
earlier constraint programming or clique approaches due to lower memory usage.

@@

A further advantage of our encoding is that it gives us efficient access to a
better branching heuristic. The CP-FC algorithm uses smallest domain first,
which in our algorithm corresponds to branching on a label class with smallest
$|T|$. We instead branch on the label class with smallest $\min(|P|,|T|)$.
This is empirically better, and accounts for much of the difference between
the number of recursive calls made; branching on the smallest $|P| |T|$ gives
very similar results. This can be viewed as exploiting both smallest domain first,
and the dual viewpoint \citep{DBLP:conf/ecai/Geelen92} of smallest domain
first, simultaneously, but we do not have the overheads of having to maintain
and channel between the dual viewpoint that would be required when using a
conventional domain store.
